Data exploration

### 2021-06-08 ms/data_exploration.Rmd
Add area to models

* `grids`: ID code for each grid cell
* `lat`: latitude of grid cell centroid
* `long`: longitude of grid cell centroid
* `richness`: number of taxa
* `pd_obs_z`: standard effect size (SES) of phylogenetic diversity (pd)
* `fd_obs_z`: SES of functional diversity (fd)
* `rpd_obs_z`: SES of relative pd
* `rfd_obs_z`: SES of relative fd
* `temp`: mean annual temperature (10 x °C)
* `precip`: total annual precipitation (mm)
* `precip_season`: seasonality in precipitation
* `percent_apo`: percent of apogamous taxa in that grid cell (repro data only)

>>>>

* `grids`: ID code for each grid cell
* `lat`: latitude of grid cell centroid
* `long`: longitude of grid cell centroid
* `richness`: number of taxa
* `pd_obs_z`: standard effect size (SES) of phylogenetic diversity (pd)
* `fd_obs_z`: SES of functional diversity (fd)
* `rpd_obs_z`: SES of relative pd
* `rfd_obs_z`: SES of relative fd
* `temp`: mean annual temperature (10 x °C)
* `precip`: total annual precipitation (mm)
* `precip_season`: seasonality in precipitation
* `area`: rolling mean of area in 0.2 degree latitudinal bands
* `percent_apo`: percent of apogamous taxa in that grid cell (repro data only)
